DATA 621 - Business Analytics and Data Mining

### 2020-11-26 HW5/HW5-Draft.Rmd
Great use of LaTeX. Some minor cleanup like using cases enviornment and using the LaTeX delimiters and not the TeX delimiters

In the ZIP model, the independent variable, $TARGET_i$, take zero values $TARGET_i \sim 0$ 
with the probability $\omega_i$ or values from Poisson distribution 
$TARGET_i \sim Pois(\lambda_i)$ with probability (1 - $\omega_i$). For $i = 1,..., n$, 
it can be written as:

\[P(Y_i = y_i) = \left\{\begin{matrix}\omega _i + (1-\omega_i)e^{-\lambda_i}), \text{ if } y_i = 0\\ (1-\omega_i)\frac{e^{-\lambda_i}\lambda_i^{y_i}}{y_i!},\text{ if } y_i > 0 \end{matrix}\right.\]

Therefore, the zero-inflated poisson model have two parameters, $\lambda_i$ and 
$\omega_i$, and linked with the predictor variables with the following:

\[log\left(\frac{\omega_i}{1-\omega_i}\right) = \sum_{j=1}^{t}\gamma_{ji}Z_{ji},\]

\[log\left(\lambda_i\right) = \sum_{j=1}^{k}\beta_{ji}X_{ji},\]

where $Z_1,..., Z_l$ are the dependent variables for the first equation and 
$X_1,..., X_k$ for the second one. The expected value and variance of the number 
of cases purchased for the $i^{th}$ wine in the ZIP model are, respectively:

\[E(Y_i) = \lambda_i(1 - \omega_i),\]

\[Var(Y_i) = (1 - \omega_i)(\lambda_i - \omega_i\lambda_i^2).\]

>>>>

In the ZIP model, the independent variable, \(TARGET_i\), take zero values
\(TARGET_i \sim 0\) with the probability \(\omega_i\) or values from Poisson
distribution \(TARGET_i \sim \mathrm{Pois}(\lambda_i)\) with probability
\((1 - \omega_i)\). For \(i = 1,\ldots, n\), it can be written as:

\[
P(Y_i = y_i) = 
\begin{cases}
\omega_i + (1-\omega_i)e^{-\lambda_i})&\text{ if } y_i = 0\\
(1-\omega_i)\frac{e^{-\lambda_i}\lambda_i^{y_i}}{y_i!}&\text{ if } y_i > 0
\end{cases}
\]

Therefore, the zero-inflated poisson model have two parameters, \(\lambda_i\)
and \(\omega_i\), and linked with the predictor variables with the following:

\[
\begin{align}
&\log\left(\frac{\omega_i}{1-\omega_i}\right) = \sum_{j=1}^{t}\gamma_{ji}Z_{ji}\\
&\log\left(\lambda_i\right) = \sum_{j=1}^{k}\beta_{ji}X_{ji}
\end{align}
\]

where \(Z_1,\ldots, Z_l\) are the dependent variables for the first equation and 
\(X_1,\ldots, X_k\) for the second one. The expected value and variance of the
number of cases purchased for the \(i^{\textrm{th}}\) wine in the ZIP model are
respectively:

\[
\begin{align}
\mathrm{E}(Y_i) &= \lambda_i(1 - \omega_i)\\
\mathrm{Var}(Y_i) &= (1 - \omega_i)(\lambda_i - \omega_i\lambda_i^2)
\end{align}
\]
